\chapter{References}

\section[Research Papers]{\textbf{Research Papers}}

\begin{enumerate}
\item Mrudul Kandalkar et al., ``Virtual Cryptocurrency Trading System,'' 2023.
\item Mohona Bhattacharya et al., ``Virtual Stock Trading Platform with Trading Tutorial,'' 2023.
\item Dr. Madhuri Chansarkar, ``Concept of Paper Trading in Stock Markets,'' 2022.
\item Sanay Khurana, ``Trading Simulation -- An Experiential Learning Tool,'' 2021.
\item Alain Finet et al., ``Trading Psychology Under Pressure: Cognitive Bias Evolution in a Simulated Bear Market,'' 2025.
\item Tomasz Rak et al., ``Performance-Based Classification of Users in a Containerized Stock Trading Application Environment Under Load,'' 2025.
\item Danylo Sereda, ``Real-Time Interaction on the Web: How WebSockets Change Application Performance,'' 2024.
\item Eko Cahyo Nugroho, ``A Horizontally Scalable WebSocket Architecture for Cost-Effective Online Examination Proctoring System on AWS Cloud Infrastructure,'' 2024.
\end{enumerate}

\section[Books]{\textbf{Books}}

\begin{enumerate}
\item Martin Kleppmann, ``Designing Data-Intensive Applications: The Big Ideas Behind Reliable, Scalable, and Maintainable Systems,'' O'Reilly Media, 2017.
\item Sam Newman, ``Building Microservices: Designing Fine-Grained Systems,'' O'Reilly Media, 2021.
\end{enumerate}

\section[Websites]{\textbf{Websites}}

\begin{enumerate}
\item Binance API Documentation -- \url{https://binance-docs.github.io/apidocs/}
\item FastAPI Documentation -- \url{https://fastapi.tiangolo.com/}
\item Redis Documentation -- \url{https://redis.io/docs/}
\item PostgreSQL Documentation -- \url{https://www.postgresql.org/docs/}
\item Next.js Documentation -- \url{https://nextjs.org/docs}
\item Zustand Documentation -- \url{https://docs.pmnd.rs/zustand}
\item KLineCharts Documentation -- \url{https://klinecharts.com/}
\item Google OAuth 2.0 Documentation -- \url{https://developers.google.com/identity/protocols/oauth2}
\item Cashfree Documentation -- \url{https://docs.cashfree.com/}
\item Brevo SMTP Documentation -- \url{https://developers.brevo.com/}
\item Docker Documentation -- \url{https://docs.docker.com/}
\end{enumerate}


